---
title: "README"
output:
  md_document:
  variant: markdown_github
---
  
  ## Load Dataset
  
  The necessary libraries and the wine dataset are loaded.

```{r load-data}
library(tidyverse)

data_url <- 'https://raw.githubusercontent.com/koimabrian/Datasets/refs/heads/main/Wine.csv'
Wine <- read.csv(data_url, comment = "#")  # Handle potential comments in the CSV
head(Wine)
```

## Standardize Continuous Variables

The continuous variables (excluding observation number and country) are scaled.

```{r standardize-data}
data <- Wine %>% select(-Obs, -Country) %>% scale()
```

## Create Clusters with K-Means

The k-means algorithm is applied to the standardized data, setting the number of clusters to 3.

```{r kmeans-clustering}
kmeans_result <- kmeans(data, centers = 3, iter.max = 100, nstart = 100)
kmeans_result
```

## Determine the Optimal Number of Clusters

To identify the optimal number of clusters, the within-cluster sum of squares (WSS), silhouette method, and gap statistic are visualized.

```{r optimal-cluster-number, warning=FALSE, message=FALSE}
library(factoextra)
# WSS plot
fviz_nbclust(data, kmeans, method = "wss")

# Silhouette plot
fviz_nbclust(data, kmeans, method = "silhouette")

# Gap statistic
fviz_nbclust(data, kmeans, method = "gap_stat")
```

## Cluster Visualization

Clusters are visualized in a biplot, and then plotted using the original variables (Rating vs Price).

```{r cluster-biplot, warning=FALSE, message=FALSE}
# Cluster biplot
fviz_cluster(kmeans(data, centers = 3, iter.max = 100, nstart = 100), data = data)
```

### Clusters with Original Variables

Cluster labels are added to the original dataset, and clusters are visualized using the Rating and Price variables.

```{r original-variable-clusters, warning=FALSE, message=FALSE}
clusters <- kmeans(data, centers = 3, iter.max = 100, nstart = 100)
Wine <- Wine |> mutate(cluster = clusters$cluster)

# Plot clusters using Rating and Price
Wine |> ggplot(aes(x = Rating, y = Price, col = as.factor(cluster))) + 
  geom_point() + 
  labs(title = "Wine Clusters by Rating and Price", color = "Cluster")
```
